A secondary screen architecture to accurately capture viewer interactions in interactive TV environments

### 2014-04-30 src/paper.tex
Paper updated

The traditional remote control as a mechanism of interaction between viewer and TV can present some problems. Since watching TV is a social and collective experience it is difficult to automatically identify the viewer in charge of the remote control. In addition, explicit interactions that require the use of the main screen of the TV set (e.g., evaluate the current content or read comments) ends up interfering in the collective experience. Some researchers tried to address this problem

provide services which deliver personalized content to both individual users and groups of users. Such services depend on user preferences, which can be obtained by observing past viewers interactions with the TV system.

@@

TV family behaviors towards television.
potential of mobile devices to capture individual user interactions.

@@

>>>>

The traditional remote control as a mechanism of interaction between viewer and TV can present notable problems.It is difficult to automatically identify the viewer in charge of the remote control. Thus, in practice the captured interactions are assigned to the whole group, rather than to individual viewers. As a result, in recommender systems applications for example, the tastes of the user in charge of the remote control can be imposed on the tastes of others.

Considering the collective experience of watching TV, the explicit interactions of one viewer can potencialy interfere in the experience of other viewers. Since there is only one remote control and a unique screen (TV screen), explicit interactions that require the use this screen (e.g., evaluate the current content or read viewers comments) end up in an undesired experience for users that are not actively participating of that interactions.

The proliferation of personal mobile devices has changed the people behaviors towards TV. Frequently people perform secondary tasks while watching TV such as use of email, use of social networks or surf the web. Many times these tasks are related to television watching where the viewer can evaluate, share or even recommend content to other people. Following this trend, more and more TV providers are enabling the audience to use personal devices as an extension of TV, i.e., as a secondary screen to enrich and immerse the user into the TV experience.

Identifying the viewers and capturing their interactions in TV environments are challenging activities~\cite{Hwang2007,Teixeira2010}.

@@

TV family behaviors towards television.
potential use of mobile devices to capture individual user interactions.

@@

\section{Architecture}

\section{Conclusions}
